\documentclass[11pt]{article}
\usepackage[letterpaper,margin=0.68in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tgheros}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{microtype}
\usepackage[svgnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{ragged2e}
\usepackage{etoolbox}

\newcommand{\newflag}[2]{%
  \newtoggle{#1}%
  \ifstrequal{#2}{true}{\toggletrue{#1}}{\togglefalse{#1}}%
}
\newcommand{\IF}[2]{\iftoggle{#1}{#2}{}}
\newcommand{\IFNOT}[2]{\iftoggle{#1}{}{#2}}
\newcommand{\IFELSE}[3]{\iftoggle{#1}{#2}{#3}}

% Flags to include or exclude parts of the resume
\newflag{TAGLINE}{true}   % if we want a tagline on the resume
\newflag{SUMMARY}{true}   % if we want a summary block on the resume
\newflag{SKILLS}{true}    % if we want a skills block on the resume

\newflag{MF}{true}        % if we are targetting mainframe modernization jobs
\newflag{EMBEDDED}{true}  % if we are targetting firmware/embedded jobs
\newflag{COMPILER}{true}  % if we are targetting compiler-related jobs

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setstretch{1.05}
\definecolor{accent}{HTML}{0F2740}
\definecolor{textgray}{HTML}{222222}
\definecolor{muted}{HTML}{4B5563}

\titleformat{\section}
  {\Large\bfseries\color{accent}}
  {}
  {0pt}
  {}
  [\vspace{3pt}{\color{accent}\titlerule[0.8pt]}]
\titlespacing*{\section}{0pt}{12pt}{8pt}

\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=3pt,
  topsep=4pt,
  parsep=0pt,
  partopsep=0pt
}

\newcommand{\resheader}[1]{\section*{#1}\vspace{-4pt}}
\newcommand{\jobheading}[4]{%
  \vspace{6pt}\begin{tabularx}{\textwidth}{@{}X r@{}}
    {\textbf{#1}} & {\textbf{#2}} \\
    {{\normalsize #3}\hspace{0.5em}{\color{muted}·}\hspace{0.5em}{\color{muted}#4}} & {} \\
  \end{tabularx}\vspace{2pt}
}

\begin{document}

{\centering
  {\fontsize{21}{23}\selectfont\bfseries GEORGE TATAR}\\[8pt]
  \IF{TAGLINE}{{\normalsize\color{accent}Principal-level software engineer \textbar\ 25 years in distributed systems, storage, and cloud migration\\}}%
  {\normalsize\color{textgray}Needham, MA \textbar\ (617) 515-9081 \textbar\ \href{mailto:gtatar@tatar-family.com}{gtatar@tatar-family.com}}\\
\par}

\IF{SUMMARY}{%
  \resheader{SUMMARY}

  25 years building systems where correctness and performance matter. This work includes developing automated mainframe-to-cloud code conversion platforms at Amdocs, leading an 8-engineer team migrating a .NET monolith to AWS microservices that run 5 global factories at Cimpress, and engineering storage-virtualization data-path internals (b-trees, GC, on-disk layout, cross-DC replication) at Actifio.
}%

\IF{SKILLS}{%
  \resheader{SKILLS}

  \begin{itemize}
  \IFNOT{SUMMARY}{\item Principal/Staff IC across distributed systems, storage, cloud platforms, and legacy modernization.}%
  \item Backend \& systems: Java, C\#, C++, C, Python --- performance-critical and data-integrity-critical code.
  \item Cloud \& distributed: AWS (EC2, RDS, S3, CloudFront, CloudFormation, EKS), Kubernetes, Docker, microservices, REST, OAuth 2.0.
  \item Databases: PostgreSQL, Microsoft SQL Server, Oracle, MariaDB; SQL and ETL tooling.
  \item Frameworks \& runtimes: .NET Core, Spring, Tomcat, Hibernate.
  \item Systems \& embedded: Linux, firmware, device drivers, Android, Bluetooth.
  \item Also: JavaScript, HTML, CSS, SQLite, WPF, WCF, IIS, .NET Framework, Windows Server, \IF{MF}{COBOL, JCL, DB2, CICS,} SAN, iSCSI, Fibre Channel, SOAP, XML, JSON, YAML, CI/CD.
  \end{itemize}
}%

\resheader{EXPERIENCE}

\jobheading{AMDOCS}{2023-present}{\IFELSE{MF}{Mainframe Modernization Engineer}{Cloud Migration Engineer, Platform \& Tooling}}{Remote}
\begin{itemize}
\item Architect and implement core components of an automated mainframe-to-cloud migration platform.
\item Build code conversion tools that transform millions of lines of legacy applications into functionally equivalent C\# or Java systems.
\item Develop ETL tooling to migrate schemas and data from legacy databases to modern SQL platforms, including SQL Server, Oracle, and PostgreSQL.
\item Develop Java and C\# compatibility libraries that emulate mainframe features on Linux and Windows.
%\item Designed the containerized runtime platform for migrated workloads, packaging converted C\# and Java services with Docker and deploying them to Kubernetes on Amazon EKS.
\item C\#, Java, SQL Server, Oracle, PostgreSQL.
\end{itemize}

\jobheading{ZYRLO}{2021-2023}{Software Architect}{Sudbury, MA}
\begin{itemize}
\item Defined the software architecture and implemented core system components for an assistive device for visually impaired users.
\item Architected and built the software stack around the main CM4 controller running Ubuntu Core, with an SD410/Android subsystem for braille and accessibility, and ESP32 firmware.
\item Implemented the key software and hardware interfaces across the product stack, including custom protocols, Bluetooth, Android integration, and Linux drivers.
\item Worked with hardware engineers on schematic reviews, board bring-up, and hardware/software debugging, including bootloader configuration and driver integration.
\item Technologies: C, C++, Python, Ubuntu Core, Android, Bluetooth, device drivers.
\end{itemize}

\jobheading{AKRUTO, INC}{2019-2021}{Founder}{Needham, MA}
\begin{itemize}
\item Founded and operated AkrutoSync, a commercial software product that synchronized Microsoft Outlook contacts and calendars with smartphones for paying customers.
\item Reimplemented Microsoft Exchange synchronization protocols from documentation and observed Exchange Server behavior, including SOAP and XML message handling and OAuth 2.0 support for Microsoft 365 modern authentication.
\item Designed and implemented the core synchronization engine as a Windows desktop application (C\#/WPF, .NET Framework, SQLite)
\item Built and operated the customer-facing website (JavaScript/HTML/CSS) along with a license and auto-update service (.NET Framework) for the installed desktop clients, driven by a CI/CD pipeline for automated releases.
\item Owned product delivery and business operations end to end, including billing via Stripe, customer support, and management of contractors for marketing and technical support.
\end{itemize}

\jobheading{CIMPRESS/VISTAPRINT}{2013-2019}{Lead Software Engineer}{Waltham, MA}
\begin{itemize}
\item Led an 8-engineer team within a 1,000-engineer organization in a company-wide initiative to migrate a legacy .NET/WPF/SQL Server monolith to a modern RESTful microservices architecture on AWS (.NET Core on Ubuntu, MariaDB).
\item Architected the microservices for our team's domains and developed mission-critical software driving end-to-end operations across 5 global factories (consumer order processing, production scheduling, supply chain, worker shifts, and shipping).
\item Owned the full lifecycle of these distributed microservices—from system design to DevOps—driving a gradual decoupling strategy, building CI/CD pipelines for automated deployment, and managing cloud infrastructure using CloudFormation, EC2, RDS, S3, and CloudFront.
\item Later containerized the .NET Core services with Docker and migrated the fleet from EC2-hosted deployments onto Amazon EKS, standardizing Kubernetes-based deployments, rolling updates, and horizontal autoscaling across the 5-factory production footprint.
\item Owned direct integration with new manufacturing equipment, including commercial digital presses and embroidery machines.
\item Drove the evaluation and implementation of OAuth 2.0 with Auth0 to secure authentication and authorization across the new microservices architecture.
\end{itemize}

\jobheading{DESKTONE, INC}{2012-2013}{Engineering Lead}{Lexington, MA}
\begin{itemize}
\item Engineering lead for a Desktop-as-a-Service product delivering virtual machines through private and public cloud.
\item Led the conversion from a single-datacenter system to a multi-datacenter architecture, including PostgreSQL replication, cross-DC communication, and failover/failback.
\item Provided technical leadership and mentoring for junior team members.
\item Defined a redundant multi-datacenter design with pairs of each node type in every datacenter.
\item Java, Tomcat, Spring, Hibernate, Ubuntu Linux, PostgreSQL, Python.
\end{itemize}

\jobheading{ACTIFIO, INC}{2009-2012}{Architect}{Waltham, MA}
\begin{itemize}
\item Architected and developed system-level components for Actifio's storage virtualization appliance.
\item Designed core data-path subsystems including b-trees, indexes, garbage collection, on-disk data layout, and offsite backup and restore.
\item Built code in the block-IO path, where correctness of every IO and sub-millisecond latency were hard requirements.
\item Designed a high-throughput TCP-based protocol to duplicate data between datacenters.
\item C++, SUSE Linux, Fibre Channel, iSCSI, SAN.
\end{itemize}

\jobheading{APPIQ, INC. (acquired by HP in 2005)}{2001-2009}{Software Engineer, Sr Software Engineer, Principal Software Engineer}{Marlborough, MA}
\begin{itemize}
\item Led Sustaining Engineering team for 2 years. Handled customer escalations, assigned support cases, monitored progress, worked with support organization and directly with customers. Found ways to make the product easier to support.
\item Worked with SNIA (Storage Networking Industry Association). Participated in SNIA plugfests. Demonstrated Storage Essentials product at the SNW (Storage Networking World).
\item On the Storage Essentials Advanced Development team, helped reengineer the product for scale-out, tolerance to SAN problems, and an improved user interface.
\item Built the storage system provider framework used to add device support, created storage system providers, and mentored new team members.
\item Java, JBoss, Tomcat, Spring, Windows, SunOS, Red Hat Linux, Oracle, SMI-S, Fibre Channel, iSCSI, SAN.
\end{itemize}

\resheader{EDUCATION}

\jobheading{HARVARD UNIVERSITY EXTENSION SCHOOL}{2005}{Master of Liberal Arts, Information Technology}{Cambridge, MA}

For master's thesis, wrote a C compiler front end and code generator.

Was able to parse the entire source code for the Apache web server into an internal representation, convert from internal representation back to C code, then compile it and use the web server.

\end{document}
